Reformulating phylogenetic mixed models to improve flexibility and speed

### 2019-04-09 phyloglmm_ms.tex
filled in all figure and table captions

There are two general challenges in linking the evolutionary process to a phylogenetic comparative statistical framework.
% Phylogenetic signal : the magnitude of phylogenetic correlation
The first challenge is to identify and separate phylogenetic signals from other sources of variation present in the data \citep{blomberg2003testing}.  
% \bmb{prev sentence doesn't seem be quite the right lead-in to the rest of the paragraph? You go on to talk about the tip-variation/residual-variation confounding issue. Maybe replace with something talking more specifically about resolving tip variation?}
The classic phylogenetic regression uses a statistical model that is equivalent to assuming that phylogenetic correlation in the residuals from a regression between two species-level traits arises because the residual variation in the trait that is the dependent variable evolves along the branches of the phylogeny according to a Brownian-motion evolutionary model. 
If the residuals are normally distributed and observed without any additional error or within-species variation, Felsenstein's method of phylogenetically independent contrasts (PICs) \citep{felsenstein1985phylogenies, nicolakakis2000forebrain} is sufficient to account for the phylogenetic correlation.
More recent approaches -- including phylogenetic generalized linear mixed models (PGLMM) \citep{ives2011generalized}, Pagel's $\lambda$ \citep{pagel1999inferring}, and Blomberg's $K$ \citep{blomberg2003testing} --- build upon PICs by considering different (non-Normal) response distributions and by accounting for additional complexities in the evolutionary process. 
In particular, they can partition residual variation into (1) uncorrelated, or independent, residual variation (observation error or tip variation) and (2) phylogenetic signal  (biological/evolutionary process error) \citep{hansen2012interpreting}.
However, if each species' traits are observed more than once, possibly under different conditions, we can potentially distinguish third level of variation; in this case, phylogenetic signal and tip variation are now both part of the evolutionary process error (which we will call intercept-level variation) while the among species residual error is associated with among observations variation within each species.
%\bmb{This is a good point, well expressed. Does PGLMM lump tip variation and within-species variation, or is this primarily an issue with Blomberg/Pagel? Thinking about Boettiger's critique \cite{boettiger2013is} (don't know if it's been peer-reviewed, we could ask him), which might be resolved if we think explicitly about within-species variation \ldots
%\mli{I think it is more like our simulation test. In Boettiger's example, it is treating sister taxa as different species. So it is using a phylogenetic tree of 8 species instead of 4.}
Although many studies include multiple observations per species, phylogenetic analyses rarely take advantage of such observations to partition variability more finely.
Indeed, many existing methods cannot accommodate multiple observations per species, instead requiring users to collapse the data by taking species averages.
%Despite having multiple observations per tip taxon (species), a typical part of observational or experimental design, but it is rarely seen: existing platforms are unable to fit multiple observations, or unbalanced design data, or both.
% \bmb{OK, but we should be prepared to support this. Could we construct a table of existing approaches/platforms with their capabilities?}

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.8]{./phylo_diagram.png}
  \caption{Visual categorization of various forms of variation.}
\label{fig:variation}
\end{figure}
\end{center}

@@

%% FIXME: chart looks ugly
\begin{table}[]
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Model}                                                                                    & \textbf{Method}                                                       & \textbf{Data}                                                                & \textbf{Platform}                                                                              \\ \hline
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Generalized Linear \\ Model (GLM)\end{tabular}}        & Correlated residual                                                   & Single Observation                                                           & \begin{tabular}[c]{@{}l@{}}\pkg{nlme}:gls, \\ \pkg{ape}:pic\end{tabular}                                   \\ \cline{2-4} 
                                                                                                  & \begin{tabular}[c]{@{}l@{}}Residual \\ + phylo intercept\end{tabular} & Single Observation                                                           & \begin{tabular}[c]{@{}l@{}}Pagel's $\lambda$\\ Blomberg's $k$ \\ via \pkg{nlme}:gls\\ \pkg{phylolm}\end{tabular} \\ \hline
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Generalized Linear \\ Mixed Model (GLMM)\end{tabular}} & \multirow{2}{*}{Random effect}                                        & \begin{tabular}[c]{@{}l@{}}Single Observation\\ Balanced Design\end{tabular} & \pkg{pez}                                                                                            \\ \cline{3-4} 
                                                                                                  &                                                                       & Unrestricted                                                                 & \pkg{lme4}, \pkg{glmmTMB}                                                                                  \\ \hline
\multirow{2}{*}{Bayesian GLMM}                                                                    & \multirow{2}{*}{Random effect}                                        & Balanced Design                                                              & \pkg{MCMCglmm}                                                                                       \\ \cline{3-4} 
                                                                                                  &                                                                       & Unrestricted                                                                 & \pkg{brms}                                                                                           \\ \hline
\end{tabular}
\caption{Model and platforms}
\label{table:model}
\end{table}

@@

\subsection*{Phylogenetic generalized linear mixed model}
Alternatively, one can use the generalized linear mixed effects modelling (GLMM) framework \citep{lynch1991methods}.
The generalized linear mixed effect model is an extension of the classic regression model, a kind of hierarchical linear model that can flexibly incorporate more than one kind of variability through random effects and for non-Gaussian responses.
The typical GLMM has the form:
\begin{align}
\bY & \sim \mathbf{f}(\bmu) + \besp \label{eq:glmm1} \\
\bmu & = \bX \bbeta + \bZ \bb  \label{eq:glmm2} \\
\bb & \sim \textrm{MVN}(0, \bSigma(\theta)) \label{eq:glmm3} \\
\besp & \sim \textrm{N}(0,\sigma^{2}_{\epsilon})
\end{align}
where $\bZ$ is an $n \times m$ model matrix for the $n$ -- dimensional vector-valued $m$ predictor variables; $\bb$ (sometimes referred as the "G-side" effect) represents the conditional modes and assumed to be multivariate normally distributed with a variance-covariance matrix given by $\bSigma(\theta)$; $\besp$ (sometimes referred as "R" effect) is an $n \times 1$ vector of independent and normally distributed error terms with variance $\sigma_{\epsilon}^2$.
Analogously, the phylogenetic regression given by (\ref{eq:gls1}) can be represented in the generalized mixed model framework with Gaussian responses by constraining $\bSigma(\theta) = \sigma^2 \bC$ and $\sigma^{2}_{\epsilon} = 0$.

@@

% Table \mli{ref something} provides the statistically equivalent fitting capabilities of common/existing phylogenetic methods.
\begin{table}[]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Package} & \pkg{nlme} & \pkg{phylolm} & \pkg{lme4}/\pkg{glmmTMB} & \pkg{pez} & \pkg{brms} & \pkg{MCMCglmm} \\ \hline
Single Group & X & X & X &  & X & X \\ \hline
\begin{tabular}[c]{@{}c@{}}Phylo Intercept\\ Phylo Slope\\ Phylo Slope-Intercept correlation\\ Residual\end{tabular} & X & \begin{tabular}[c]{@{}c@{}}X\\ \\ \\ X\end{tabular} & \begin{tabular}[c]{@{}c@{}}X\\ X\\ X\\ X\end{tabular} &  & \begin{tabular}[c]{@{}c@{}}X\\ X\\ X\\ X\end{tabular} & \begin{tabular}[c]{@{}c@{}}X\\ X\\ X\\ X\end{tabular} \\ \hline
Multi-group &  &  & X & X & X & X \\ \hline
\begin{tabular}[c]{@{}c@{}}Phylo Intercept\\ Phylo Slope\\ Phylo Slope-intercept correlation\\ Phylo Species-group interaction\\ Species intercept\\ Species Slope \\ Species Slope-intercept correlation\\ Residual\end{tabular} &  &  & \begin{tabular}[c]{@{}c@{}}X\\ X\\ X\\ X\\ X\\ X\\ X\\ X\end{tabular} & \begin{tabular}[c]{@{}c@{}}X\\ X\\ \\ X\\ X\\ X\\ \\ X\end{tabular} & \begin{tabular}[c]{@{}c@{}}X\\ X\\ X\\ X\\ X\\ X\\ X\\ X\end{tabular} & \begin{tabular}[c]{@{}c@{}}X\\ X\\ X\\ \\ X\\ X\\ X\\ X\end{tabular} \\ \hline
\end{tabular}%
}
\caption{Parameters}
\label{table:platform}
\end{table}

\subsection*{Simulation and evaluations}
We simulated 100 phylogenetic trees for each sample size (n = 25,50,100, 500) and incorporated simulation parameters (illustrated in figure 2 and 5) to simulate responses from the simulation model (\ref{eq:ss_sim}, \ref{eq:ms_sim}).
Each realization were fitted to all model variant using different platforms.
Tables \ref{table:platform} shows the parameters that are estimable for each platform. 
We only evaluated the goodness of fit for model fits that passed the convergence tests implemented by the package.
For Bayesian GLMM, we combined two criteria to assess convergence: we required a value of the Gelman and Rubin statistic less than 1.1 and an effective sample size (ESS) greater than 1000 for the fixed effect parameters ($\beta_{0} \ \textrm{and} \ \beta_{1}$) for each replication. 
For each replication we sample two chains starting with 10000 iterations. 
%% TODO MAKE SURE THIS IS CORRECT!
We first evaluate our estimates by looking at the distribution of the estimated values (maximum likelihood estimates for non-Bayesian platforms and posterior medians for Bayesian platforms -- this gives us an idea of bias and variation (i.e. quality of the point estimate).
Then we look at frequentist coverage, to assess quality of confidence intervals.
Coverage refers to the frequency with which the computed confidence intervals include the true values of parameters.
We used 90\% (Wald and profile) confidence intervals and quantile-based intervals (for Bayesian GLMM) to evaluate coverage.
We also compare computational speed between different platforms to evaluate the efficiency of the platforms and methods.

@@

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.8,page=1]{./git_push/plot.Rout.pdf}
  \caption{New}
\label{ssplot}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.8,page=2]{./git_push/plot.Rout.pdf}
  \caption{New}
\label{ssplot}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.8,page=3]{./git_push/plot.Rout.pdf}
  \caption{New}
\label{ssplot}
\end{figure}
\end{center}

% \bmb{Need to think a little harder about the important points/order here (might be time to do the exercise where you take the results and boil them back down to short bullet points, in order to figure out whether you've said the important stuff, in the right order). Maybe lead by saying that all platforms give similar answers - to the extent that they are fitting the same statistical model (this might even be emphasized/explained above, in Methods). Am I correct in believing that phylolm=\pkg{lme4} but without intercept/slope correlation, and gls is additionally missing random slopes?}

% \begin{itemize}
% \item{full model provides good estimates (except for correlation)}
% \item{reduced models try to fit with whatever parameters they have available (over-estimates the simulation parameters)}
% \item{no slope vs slope}
% \item{no correlation vs correlation}
% \item{as size/data/number of species increase, the parameter estimates gets better}
% \item{single site models are fast}
% \item{estimates gets closer to simulation parameter as number of species increase}
% \item{lme4/tmb are fast, everything else is slow for multiple sites}
% \end{itemize}

The full fitted model (which matches the simulation model that incorporates phylogenetic intercept, slope and correlation) provides estimates with low bias and variance for all parameters. 
Estimates for fixed effect parameters ($\beta_0$ and $\beta_1$) approach nominal coverage as the number of species increases for \pkg{lme4} and \pkg{glmmTMB} but not for other packages. 
\mli{we know why brms over covers}
%% \mli{Is there a figure for this?....Ok, maybe We don't need it.}

@@

% \bmb{(2) please define ``robustness'' -- usually means lack of sensitivity to model.  Are you talking about the variance of the estimates? I'd prefer not to use ``robust'' in a non-standard way if possible (2) what are small/medium/large? I see that $n=\{20,100,500\}$ and $m=\{1,20\}$, but not sure how these match up to ``small'', ``medium'', ``large''; is Figure 1 all $m=1$? Might be worth just labeling by $n=??$ rather than using small/medium/large}
% It is unclear how different levels of phylogenetic signal are being confounded under the error free (without tip variation) assumption for the PGLS models.
% \bmb{can we figure this out, even in an empirical/crude way??? it's tough to have results without knowing the true value they're aiming for ...}

@@

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.8,page=4]{./git_push/plot.Rout.pdf}
  \caption{new}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.8,page=5]{./git_push/plot.Rout.pdf}
  \caption{new}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.8,page=6]{./git_push/plot.Rout.pdf}
  \caption{new}
\end{figure}
\end{center}

>>>>

There are two general challenges in linking the evolutionary process to a phylogenetic comparative statistical framework.
% Phylogenetic signal : the magnitude of phylogenetic correlation
The first challenge is to identify and separate phylogenetic signals from other sources of variation present in the data \citep{blomberg2003testing}.  
% \bmb{prev sentence doesn't seem be quite the right lead-in to the rest of the paragraph? You go on to talk about the tip-variation/residual-variation confounding issue. Maybe replace with something talking more specifically about resolving tip variation?}
The classic phylogenetic regression uses a statistical model that is equivalent to assuming that phylogenetic correlation in the residuals from a regression between two species-level traits arises because the residual variation in the trait that is the dependent variable evolves along the branches of the phylogeny according to a Brownian-motion evolutionary model. 
If the residuals are normally distributed and observed without any additional error or within-species variation, Felsenstein's method of phylogenetically independent contrasts (PICs) \citep{felsenstein1985phylogenies, nicolakakis2000forebrain} is sufficient to account for the phylogenetic correlation.
More recent approaches -- including phylogenetic generalized linear mixed models (PGLMM) \citep{ives2011generalized}, Pagel's $\lambda$ \citep{pagel1999inferring}, and Blomberg's $K$ \citep{blomberg2003testing} --- build upon PICs by considering different (non-Normal) response distributions and by accounting for additional complexities in the evolutionary process. 
In particular, they can partition residual variation into (1) uncorrelated, or independent, residual variation (observation error or tip variation) and (2) phylogenetic signal  (biological/evolutionary process error) \citep{hansen2012interpreting}.
However, if each species' traits are observed more than once, possibly under different conditions, we can potentially distinguish third level of variation; in this case, phylogenetic signal and tip variation are now both part of the evolutionary process error (which we will call intercept-level variation) while the among species residual error is associated with among observations variation within each species.
%\bmb{This is a good point, well expressed. Does PGLMM lump tip variation and within-species variation, or is this primarily an issue with Blomberg/Pagel? Thinking about Boettiger's critique \cite{boettiger2013is} (don't know if it's been peer-reviewed, we could ask him), which might be resolved if we think explicitly about within-species variation \ldots
%\mli{I think it is more like our simulation test. In Boettiger's example, it is treating sister taxa as different species. So it is using a phylogenetic tree of 8 species instead of 4.}
Although many studies include multiple observations per species, phylogenetic analyses rarely take advantage of such observations to partition variability more finely.
Indeed, many existing methods cannot accommodate multiple observations per species, instead requiring users to collapse the data by taking species averages.
Figure \ref{fig:variation} illustrates a visual categorization of various forms of variation for three species. 
%Despite having multiple observations per tip taxon (species), a typical part of observational or experimental design, but it is rarely seen: existing platforms are unable to fit multiple observations, or unbalanced design data, or both.
% \bmb{OK, but we should be prepared to support this. Could we construct a table of existing approaches/platforms with their capabilities?}

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.8]{./phylo_diagram.png}
  \caption{Visual categorization of various forms of phylogenetic variation of three species. Top left shows pure noise (i.e. assuming a star phylogeny); top right accounts for phylogeny, but without noise; bottom left accounts both phylogeny and noise at the tip, and finally bottom right shows multiple observations (with noise) at the tips.}
\label{fig:variation}
\end{figure}
\end{center}

@@

%% FIXME: chart looks ugly
\begin{table}[]
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Model}                                                                                    & \textbf{Method}                                                       & \textbf{Data}                                                                & \textbf{Platform}                                                                              \\ \hline
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Generalized Linear \\ Model (GLM)\end{tabular}}        & Correlated residual                                                   & Single Observation                                                           & \begin{tabular}[c]{@{}l@{}}\pkg{nlme}:gls, \\ \pkg{ape}:pic\end{tabular}                                   \\ \cline{2-4} 
                                                                                                  & \begin{tabular}[c]{@{}l@{}}Residual \\ + phylo intercept\end{tabular} & Single Observation                                                           & \begin{tabular}[c]{@{}l@{}}Pagel's $\lambda$\\ Blomberg's $k$ \\ via \pkg{nlme}:gls\\ \pkg{phylolm}\end{tabular} \\ \hline
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Generalized Linear \\ Mixed Model (GLMM)\end{tabular}} & \multirow{2}{*}{Random effect}                                        & \begin{tabular}[c]{@{}l@{}}Single Observation\\ Balanced Design\end{tabular} & \pkg{pez}                                                                                            \\ \cline{3-4} 
                                                                                                  &                                                                       & Unrestricted                                                                 & \pkg{lme4}, \pkg{glmmTMB}                                                                                  \\ \hline
\multirow{2}{*}{Bayesian GLMM}                                                                    & \multirow{2}{*}{Random effect}                                        & Balanced Design                                                              & \pkg{MCMCglmm}                                                                                       \\ \cline{3-4} 
                                                                                                  &                                                                       & Unrestricted                                                                 & \pkg{brms}                                                                                           \\ \hline
\end{tabular}
\caption{List of phylogenetic generalized linear models and R packages.}
\label{table:model}
\end{table}

@@

\subsection*{Phylogenetic generalized linear mixed model}
Alternatively, one can use the generalized linear mixed effects modelling (GLMM) framework \citep{lynch1991methods}.
The generalized linear mixed effect model is an extension of the classic regression model, a kind of hierarchical linear model that can flexibly incorporate more than one kind of variability through random effects and for non-Gaussian responses.
The typical GLMM has the form:
\begin{align}
\bY & \sim \mathbf{f}(\bmu) + \besp \label{eq:glmm1} \\
\bmu & = \bX \bbeta + \bZ \bb  \label{eq:glmm2} \\
\bb & \sim \textrm{MVN}(0, \bSigma(\theta)) \label{eq:glmm3} \\
\besp & \sim \textrm{N}(0,\sigma^{2}_{\epsilon}) \label{eq:glmm4}
\end{align}
where $\bZ$ is an $n \times m$ model matrix for the $n$ -- dimensional vector-valued $m$ predictor variables; $\bb$ (sometimes referred as the "G-side" effect) represents the conditional modes and assumed to be multivariate normally distributed with a variance-covariance matrix given by $\bSigma(\theta)$; $\besp$ (sometimes referred as "R" effect) is an $n \times 1$ vector of independent and normally distributed error terms with variance $\sigma_{\epsilon}^2$.
Analogously, the phylogenetic regression given by (\ref{eq:gls1}) can be represented in the generalized mixed model framework with Gaussian responses by constraining $\bSigma(\theta) = \sigma^2 \bC$ and $\sigma^{2}_{\epsilon} = 0$.

@@

% Table \mli{ref something} provides the statistically equivalent fitting capabilities of common/existing phylogenetic methods.
\begin{table}[]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Package} & \pkg{nlme} & \pkg{phylolm} & \pkg{lme4}/\pkg{glmmTMB} & \pkg{pez} & \pkg{brms} & \pkg{MCMCglmm} \\ \hline
Single Group & X & X & X &  & X & X \\ \hline
\begin{tabular}[c]{@{}c@{}}Phylo Intercept\\ Phylo Slope\\ Phylo Slope-Intercept correlation\\ Residual\end{tabular} & X & \begin{tabular}[c]{@{}c@{}}X\\ \\ \\ X\end{tabular} & \begin{tabular}[c]{@{}c@{}}X\\ X\\ X\\ X\end{tabular} &  & \begin{tabular}[c]{@{}c@{}}X\\ X\\ X\\ X\end{tabular} & \begin{tabular}[c]{@{}c@{}}X\\ X\\ X\\ X\end{tabular} \\ \hline
Multi-group &  &  & X & X & X & X \\ \hline
\begin{tabular}[c]{@{}c@{}}Phylo Intercept\\ Phylo Slope\\ Phylo Slope-intercept correlation\\ Phylo Species-group interaction\\ Species intercept\\ Species Slope \\ Species Slope-intercept correlation\\ Residual\end{tabular} &  &  & \begin{tabular}[c]{@{}c@{}}X\\ X\\ X\\ X\\ X\\ X\\ X\\ X\end{tabular} & \begin{tabular}[c]{@{}c@{}}X\\ X\\ \\ X\\ X\\ X\\ \\ X\end{tabular} & \begin{tabular}[c]{@{}c@{}}X\\ X\\ X\\ X\\ X\\ X\\ X\\ X\end{tabular} & \begin{tabular}[c]{@{}c@{}}X\\ X\\ X\\ \\ X\\ X\\ X\\ X\end{tabular} \\ \hline
\end{tabular}%
}
\caption{List of estimable parameters for each R package.}
\label{table:platform}
\end{table}

\subsection*{Simulation and evaluations}
We simulated 100 phylogenetic trees for each sample size (n = 25,50,100 and additional n = 500 for multi-group model) and incorporated simulation parameters (illustrated in Figure \ref{ssplot} and Figure \ref{msplot}) to simulate responses from the simulation model (\ref{eq:ss_sim}, \ref{eq:ms_sim}).
Each realization were fitted to all model variant using different platforms.
Tables \ref{table:platform} shows the parameters that are estimable for each platform. 
We only evaluated the goodness of fit for model fits that passed the convergence tests implemented by the package.
For Bayesian GLMM, we combined two criteria to assess convergence: we required a value of the Gelman and Rubin statistic less than 1.1 and an effective sample size (ESS) greater than 1000 for the fixed effect parameters ($\beta_{0} \ \textrm{and} \ \beta_{1}$) for each replication. 
For each replication we sample two chains starting with 10000 iterations. 
%% TODO MAKE SURE THIS IS CORRECT!
We first evaluate our estimates by looking at the distribution of the estimated values (maximum likelihood estimates for non-Bayesian platforms and posterior medians for Bayesian platforms -- this gives us an idea of bias and variation (i.e. quality of the point estimate).
Then we look at frequentist coverage, to assess quality of confidence intervals.
Coverage refers to the frequency with which the computed confidence intervals include the true values of parameters.
We used 90\% (Wald and profile) confidence intervals and quantile-based intervals (for Bayesian GLMM) to evaluate coverage.
We also compare computational speed between different platforms to evaluate the efficiency of the platforms and methods.

@@

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.8,page=1]{./git_push/plot.Rout.pdf}
  \caption{Comparsion of single group model parameter estimates across different R packages in Table \ref{table:platform}. The horizontal line shows the true value of the parameters in the simulation model. Models capable of fitting all parameters (\pkg{lme4}, \pkg{brms} and \pkg{glmmTMB}) fit well for all parameters.} 
\label{ssplot}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.8,page=2]{./git_push/plot.Rout.pdf}
  \caption{Comparison of speed for all fitting packages variants: layout of the packages as in Figure \ref{ssplot}}
\label{ssplot_speed}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.8,page=3]{./git_push/plot.Rout.pdf}
  \caption{Comparison of coverage probablility for fixed effect parameters. Models matching the simulation model (\pkg{lme4}, \pkg{brms} and \pkg{glmmTMB}) have coverage near the nominal value of 0.95. The black line shows the nominal coverage, and the grey ribbon the 95\% binomial confidence interval based on 100 simulated fits.}
\label{ssplot_coverage}
\end{figure}
\end{center}

The full fitted model (which matches the simulation model that incorporates phylogenetic intercept, slope and correlation) provides estimates with low bias (the difference between the parameter estimates and true simulation parameters) and variance for all parameters. 
Estimates for fixed effect parameters ($\beta_0$ and $\beta_1$) approach nominal coverage as the number of species increases for \pkg{lme4} and \pkg{glmmTMB} but not for other packages. \pkg{brms} have higher coverage than the nominal coverage at 95 \% because the prior distributions for the simulation parameters are cenetered at the true values.
%% \mli{Is there a figure for this?....Ok, maybe We don't need it.}

@@

@@

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.8,page=4]{./git_push/plot.Rout.pdf}
  \caption{Comparsion of multi group model parameter estimates across different R packages in Table 2. Annotations as in Figure \ref{ssplot}.}
  \label{msplot}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.8,page=5]{./git_push/plot.Rout.pdf}
  \caption{Comparsion of multi group model computational speed across different R packages in Table 2. Annotations as in Figure \ref{ssplot}.}
  \label{msplot_time}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[H]
  \includegraphics[scale=0.8,page=6]{./git_push/plot.Rout.pdf}
  \caption{Comparsion of multi group model coverage across different R packages in Table 2. Annotations as in Figure \ref{ssplot}.}
  \label{msplot_coverage}
\end{figure}
\end{center}
